---
title: "Data Manipulation Exercises"
author: "Joscelin Rocha-Hidalgo"
output: 
    html_document:
        css: slides/style.css
        toc: true
        toc_depth: 1
        toc_float: true
        df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Packages

Load the `tidyverse` package.

```{r}
#load the package here:

-----------
  
```

# Import data: chds6162_data

Import the chds6162_data to a dataframe called `data`. 

```{r}

data <- -----------------
  
```


# Exercise
1. Use `filter` to only include those age younger than 40
2. Use `mutate` to transform the `gestation` variable into weeks rather than days and to create a new column called `age_group` with codes as "20s", "30s", and so on. 
* tip= Wanna know the range of your sample age? Use `range(dataframe$variable,na.rm = TRUE)`
** Use `%in%` (you just learned it 😉)
4. Use `summarise` to calculate a new variable called `mean_gestation_w` by moms `age_group` and `ed`
5. Assign it to a new data frame called `mothers_below40`
6. Export it as a csv!

Bonus: Once you have that data frame move the columns around using **"relocate"**


## Write Solution Here:
```{r}
# Run this line to check the range of the age column
range(data$age,na.rm = TRUE) 

#Write solution here:
----------

```

#### Let's take a look your new dataframe before you export it as csv 
```{r}
## Check your dataframe here
mothers_below30

#Export your dataframe as a csv
--------
  
##Check for your CSV in the exports folder
```

### With Bonus:

```{r}
#Write solution here + bonus:
--------------
  
  
#Export your dataframe as csv:
---------------
  
  
```


### Extra bonus:

- We just heard back from our collaborators and they need the mean of all the variables for dad by their race category (dads'). 

- Use `across` to get them all!

* Don't forget to remove NAs otherwise it will yell at you!

```{r}
data %>% 
  -------------------------
  
```


