---
title: "Data Manipulation Exercises"
author: "Joscelin Rocha-Hidalgo"
output: 
    html_document:
        css: slides/style.css
        toc: true
        toc_depth: 1
        toc_float: true
        df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Packages

Load the `tidyverse` package:

```{r}
library(tidyverse)
```

# Import data: chds6162_data

Import the chds6162_data to a dataframe called `data`. 

```{r}
data <- read_csv("data/chds6162_data.csv")
```


# Exercise
1. Use `filter` to only include those age younger than 40
2. Use `mutate` to transform the `gestation` variable into weeks rather than days and to create a new column called `age_group` with codes as "20s", "30s", and so on. 
* tip= Wanna know the range of your sample age? Use `range(dataframe$variable,na.rm = TRUE)`
** Use `%in%` (you just learned it 😉)
4. Use `summarise` to calculate a new variable called `mean_gestation_w` by moms `age_group` and `ed`
5. Assign it to a new data frame called `mothers_below40`
6. Export it as a csv!

**Bonus:** Once you have that data frame move the columns around using **"relocate"**


## Solution
```{r}
range(data$age,na.rm = TRUE) 

mothers_below30 <- data %>% 
    filter(age < 40) %>% 
    mutate(gestation_w = gestation/7,
            age_group = case_when(
              age %in% 10:19 ~ "10s",
              age %in% 20:29 ~ "20s",
              age %in% 30:39 ~ "30s"
              )) %>%
  group_by(age_group,ed) %>% 
  summarize(mean_gestation_w = mean(gestation_w,na.rm = TRUE))
```

#### Let's take a look your new dataframe before you export it as csv 
```{r}
mothers_below30

write_csv(mothers_below30,"exports/moms_under30.csv")

##Check for your CSV in the exports folder
```

### With Bonus:

```{r}
mothers_below30 <- data %>% 
    filter(age < 30) %>% 
    mutate(gestation_w = gestation/7) %>%
    group_by(ed) %>% 
    summarize(mean_gestation_w = mean(gestation_w,na.rm = TRUE)) %>%
    relocate (mean_gestation_w, .after=ed)

write_csv(mothers_below30,"exports/moms_under30.csv")
```


### Extra bonus:

- We just heard back from our collaborators and they need the mean of all the variables for dad by their race category (dads'). 

- Use `across` to get them all!

* Don't forget to remove NAs otherwise it will yell at you!

```{r}
data %>% 
  drop_na(drace) %>%
  group_by(drace) %>%
  summarize(across(dage:dwt,mean,na.rm = TRUE))
```


